---
title: "Assignment 1"
output: html_document
---

## **Load Libraries**
```{r}

library(dplyr)
library(ggplot2)
library(readr)

```
<br>

## **Import Data**
```{r}

Cereals <- read_csv("Cereals.csv")

```
*Data sourced from Canvas (also found at https://sites.calvin.edu/scofield/data/cereals.html).*

<br>

## **Descriptive Statistics**

### Quantitative Variables
```{r}

Cereals %>%
  select(calories, protein, fat, sodium, fiber, carbo, sugars, potass, vitamins, weight, cups, rating) %>%
  summary()

```
### Qualitative Variables
#### Manufacturer:
*A = American Home Food Products; G = General Mills; K = Kelloggs; N = Nabisco; P = Post; Q = Quaker Oats; R = Ralston Purina*
```{r}

table(Cereals$mfr)

```
#### Type:
*C = Cold; H = Hot*
```{r}

table(Cereals$type)

```
#### Display Shelf:
*1, 2, or 3, counting from the floor*
```{r}

table(Cereals$shelf)

```
<br>

## **Transform a Variable**
#### Turning type into a binary:
```{r}

# Before Transform
print(Cereals)
Cereals <- Cereals %>%
  mutate(is_cold = type == "C") %>%
  select(name, mfr, is_cold, everything(), -type)

table(Cereals$is_cold)
# After Transform
print(Cereals)

```
<br>

## **Visualize Data**
### Qualitative Variable
```{r}

ggplot(Cereals, aes(x = mfr)) +
  geom_bar(fill = "lightblue", color = "black") +
  labs(
    title = "Cereal Manufacturers",
    x = "Manufacturer",
    y = "Count"
  ) +
  theme_minimal()

```
<br>
*A = American Home Food Products; G = General Mills; K = Kelloggs; N = Nabisco; P = Post; Q = Quaker Oats; R = Ralston Purina*

### Quantitative Variables
```{r}

ggplot(Cereals, aes(x = sugars, y = rating)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_smooth(method = "lm", color = "red") +
  labs(
    title = "Sugars vs Rating",
    x = "Sugars",
    y = "Rating"
  ) +
  theme_minimal()

```
<br>
*Sugars = grams of sugars; Rating = percentage rating of the cereals*

